\documentclass[11pt]{moderncv}  % Sets the default text size to 11pt and class
                               % to article.
% moderncv themes
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{casual}

% color options 'blue' (default), 'orange', 'green', 'red', 'purple',
% 'grey' and 'black'
\moderncvcolor{blue}

% to set the default font; use '\sfdefault' for the default sans serif font,
%   '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}

% uncomment to suppress automatic page numbering for CVs longer than one page
%\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% if you want to change the width of the column with the dates
%\setlength{\hintscolumnwidth}{3cm}

% for the 'classic' style, if you want to force the width allocated to your
%   name and avoid line breaks. be careful though, the length is normally
%   calculated to avoid any overlap with your personal info; use this at your
%   own typographical risks...
%\setlength{\makecvtitlenamewidth}{10cm}
%% recipient data
\recipient
{Disney Streaming Services}
{1540 Broadway, New York, NY 10036}

% personal data
\name{John}{Evans}

%\title{Resumé title}
% optional, remove / comment the line if not wanted

\address{1735 S Street NW}{Washington, DC  20009}{USA}
\phone[mobile]{+1~(617)~447~0030}                   
\email{john.g.evans.ne@gmail.com}                  
\social[twitter]{johnevans007}                    
\social[github]{quintusdias}                     
%\extrainfo{additional information}             

%\photo[64pt][0.4pt]{picture}
% optional, remove / comment the line if not wanted.
% '64pt' is the height the picture must be resized to,
% 0.4pt is the thickness of the frame around it (put it to 0pt for no frame)
% and 'picture' is the name of the picture file

\hyphenation{MATLAB}

%-------------------------------------------------------------------------------
%            content
%-------------------------------------------------------------------------------
%            content
%-------------------------------------------------------------------------------
\begin{document}
%%-----       letter       ----------------------------------------------------
\opening{Dear sirs,}
\closing{Sincerely,}

% use an optional argument to use a string other than "Enclosure", or redefine
% \enclname
%\enclosure[Attached]{curriculum vit\ae{}}

\makelettertitle

I would like to place my name into consideration for the Data
Engineer position at Disney.  Although most of my work experience
has been more on the IT side of scientific institutions, I'm a quick
learner and feel I have a great deal to offer.  
I've recently been trying to bolster my data science / machine learning
credentials through online courses at EdX, and I am very much interested
in a roll that draws on both my existing skill set as well as machine learning. 

Python became my language of choice over the last few years and was
my primary tool working in GIS Dissemination at the National Weather
Service.  This involved such tasks as analyzing Apache log files,
writing monitoring scripts, running JMeter load tests, and more.
Monitoring 24/7 was the primary focus of the position, however.

I also have a long history with MATLAB.  In 2007, I joined the Image
and Scientific Data Formats team at the MathWorks, becoming  team
lead after one year.  This give me a broad experience with a variety
of open source image and scientific data formats and APIs, ranging
from older “classic” formats such as JPEG, FITS, TIFF, and HDF4,
to newer and more complex formats such as JPEG2000 and HDF5/netCDF.
In fact, my first assignment at MathWorks was to implement official
netCDF support in MATLAB, and this was largely based upon the earlier
netCDF community project on SourceForge, MEXCDF, to which I was the
prime contributor.   I also authored the R2011a “high-level” HDF5
interface for MATLAB while continuing to refactor and performance-tune
the existing “low-level” HDF5 interface.

Working at the MathWorks was a good experience in software engineering
practices such as continuous integration, refactoring, requirements
gathering, functional design, design reviews including test plans,
and long-range planning as the team lead.   There were not too many
opportunities for conferences, but for six years I did attend the
NASA/HDF Spring Workshop as MathWorks’ representative, where I
became well-acquainted with the people of the HDF5 Group.

Before coming to the MathWorks, I was at the School for Marine
Sciences at Rutgers University where I was responsible for managing
a small cluster used for running physical oceanographic models
(ROMS).  This required managing  netCDF output files, providing
general software support, usually in MATLAB but also in shell
scripting, maintaining a THREDDS/OpENDAP server, and general Linux
system administration.

Thank you for your consideration.  Please do not hesitate to contact
me if you require any further information.

\makeletterclosing

\end{document}


%% end of file `template.tex'.
