\documentclass[11pt]{article}  % Sets the default text size to 11pt and class
                               % to article.
\usepackage{url}
%------------------------Dimensions--------------------------------------------
\topmargin=0.0in      % length of margin at the top of the page
                      % (1 inch added by default)
\oddsidemargin=0.0in  % length of margin on sides for odd pages
\evensidemargin=0in   % length of margin on sides for even pages
\textwidth=6.5in      % How wide you want your text to be
\marginparwidth=0.5in
\headheight=0pt       % 1in margins at top and bottom (1 inch is added to this
                      % value by default)
\headsep=0pt          % Increase to increase white space in between headers
                      % and the top of the page
\textheight=9.0in     % How tall the text body is allowed to be on each page

\begin{document} 
% These two pieces of code tell LaTeX that everything that goes in
% between these tags is what you want displayed as your actual document.

% Makes whatever text you put in parenthesis move to the center
\centerline{{\Huge \sc John Evans}  } 

% Prevents the following text from being indented
% This is the same as a return in Latex
\centerline{27 Quissett Avenue.
            \textbullet \hspace{5pt} Woods Hole, MA  02543
            \textbullet \hspace{5pt}  (617) 447-0030} 
\centerline{john.g.evans.ne@gmail.com} 
\noindent
\line(1,0){470}  \\

% Don’t indent this line and make it bold and large
\noindent {\Large \bf Objective}

% This creates a small gap but not quite as large as a return (it’s
% a space saver)
\smallskip

\noindent
A development position in data science involving Python.\medskip

% This makes a large line-skip (\smallskip is also a command but has
% a smaller gap
\bigskip
\noindent{\Large \bf Special Skills}\\ 
\begin{description}
  \item[Computer Languages]Strong in Python (Numpy, Pandas, Matplotlib), strong
    in MATLAB, C/C++.  Familiar with XMP/XML.  Past experience with Java, PHP,
    bash, SQL, \LaTeX, Perl, Fortran 77, Fortran 90.
  \item[Software Practices]Experience with continuous integration, writing
    test plans, unit testing (Python and MATLAB), and software version control
    packages such as Git, Subversion, Perforce, and CVS.
  \item[Open Source]Projects on GitHub and SourceForge
    \begin{description}
      \item[Glymur]\url{http://glymur.readthedocs.org}
      \item[Mexcdf]\url{http://mexcdf.sourceforge.net}
      \item[SunPy]\url{http://www.sunpy.org} (collaborator)
      \item[Python XMP Toolkit]\url{http://python-xmp-toolkit.readthedocs.org}
        (collaborator)
    \end{description}
  \item[File Formats and Software Packages]Extensive experience with netCDF,
    HDF5, HDF4, JPEG2000, CFITSIO, libTIFF, CDF, DICOM, NRRD, and
    NIfTI.  Some experience with OpenJPEG, Kakadu, and IJG JPEG
    libraries.  Several years of MySQL database administration,
    some experience with PostgreSQL, Oracle, SQLite.
  \item[Platforms and System Administration]Currently working with CentOS,
    Fedora, and Mac OS X.  Past experience configuring Mandriva, Scyld, Ubuntu,
    Digital Unix, Irix, Windows.  Past experience configuring Samba, Amanda,
    Apache, rsync, iptables, FLEXLM.
  \item[Foreign Languages]Some familiarity with German and French.
\end{description}

\bigskip 
\noindent{\Large \bf Experience}\\ 
\begin{description}
  \item[Programmer] Integrated Statistics/NOAA, July 2014 -- present.
    Database programming support for recreational fisheries assessments
    at the Northeast Fisheries Science Center. Wrote Django frontend
    for iteractive exploration of scallops population model.
  \item[Programmer] Partners/Massachusetts General Hospital, February 2013 --
    June 2014.  Rewrote software pipelines for processing diffusion and
    DCE medical imaging data.  Performed exploratory work on platforms
    such as HubZero  for comparing algorithm performance. Wrote
    documentation and analysis tools for disease propagation model.
  \item[Developer] MathWorks, February 2007 -- October 2012.  Team lead for
    Image and Scientific Data Formats.  Delivered new MATLAB functionality
    for netCDF, HDF5, JPEG2000, HDF, HDF-EOS, FITS, TIFF, and CDF formats,
    including both high-level and low-level interfaces.  Also responsible
    for day to day maintenance of existing support for JPEG, PNG, GIF
    and various other image formats.  Delivered netCDF formal interface
    feature into MATLAB R2008b release, updated for netCDF-4 support
    in R2010b. Triaged bug reports, improved code coverage and quality,
    and managed 3rd party library integration and general infrastructure
    of my team's particular software component.  Wrote and presented
    6-month team planning documents to company management.  Sponsored
    five short-term intra-company internship projects for new engineers.
    Represented MathWorks at annual HDF/NASA Spring Workshops.
  \item[Computing Specialist] Rutgers University, September 2004 --
    February 2007. Assisted in setup,  operation, and output analysis  of
    Regional Ocean Model System (ROMS) on various OpenMP and MPI systems.
    This included operational support of a Beowulf Cluster with 20 dual
    processor compute nodes, system administration for a number of Linux
    workstations and laptops, administration of a tomcat server.
  \item[Computing Specialist] USGS, September 2003 -- August 2004.  
    Conversion of aging geographic datasets into ESRI grid and shape
    file formats and Created GIS of Gulf of Mexico datasets.
  \item[Computing Specialist] University of Maine, September 2001 -- August
    2003.  Designed and implemented a near real-time buoy processing
    system for data telemetered via both cell phone and GOES satellite
    for GoMOOS (Gulf of Maine Ocean Observing System).   The array
    of instruments included wind sensors, ADCPs, current meters,
    conductivity/temperature recorders, accelerometers, radiometers,
    and fluorometers.   Responsible for MySQL database administration
    and general systems administration of a small network of RedHat
    Linux workstations, Windows PCs, and Macs.   Wrote documentation
    for the processing system and system administrative efforts.
    Also participated in CODAR project for assimilation of RADAR into
    surface current patterns.
  \item[Software Engineer] AER, September 1998 -- July 2000.  Supported the
    Land Cover, Albedo, NDVI/EVI, and Imagery Environmental Data Records
    (EDRs) within the VIIRS project. Integrated new algorithms with
    legacy codes. Wrote gridding routines for sensed data to various
    common map projections.
  \item[Computing Specialist] USGS, May 1995 -- August 1998.  
    Wrote support software for scientific visualization, modeling, and
    public education. Conversion of old time series data sets into
    standardized netCDF conventions.  Systems administration of Linux,
    Windows, Digital Unix, and Irix systems.
\end{description}

\bigskip 
\noindent{\Large \bf Education}\\ 
\begin{description}
  \item[Master of Science] Computer Science, Montana State University, Bozeman,
    MT, May 1995.
  \item[Master of Science] Mathematics, Montana State University, Bozeman,
    MT, June 1990.
  \item[Bachelor of Science] Applied Mathematics, Montana State University,
    Bozeman, MT, June 1988.
\end{description}

\bigskip 
\noindent{\Large \bf Volunteer Activities}\\ 
\begin{description}
  \item[Zooniverse] Participant in Andromeda, Planet Hunters projects.
  \item[Running Clubs] Assisting in maintenance of Falmouth Track Club and
    Raritan Valley Road Runners web sites.  Volunteer and MIT track meets.
    President of Somerville Road Runners, June 1998 -- March 1999.
  \item[MSU Athletics] Statistician for Montana State University men's and
    women's basketball teams.
  \item[Museum of the Rockies] Helped in front desk, education, and exhibit
    construction duties.
\end{description}
\end{document} 

% moderncv themes
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{casual}

% color options 'blue' (default), 'orange', 'green', 'red', 'purple',
% 'grey' and 'black'
\moderncvcolor{blue}

% to set the default font; use '\sfdefault' for the default sans serif font,
%   '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}

% uncomment to suppress automatic page numbering for CVs longer than one page
%\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% if you want to change the width of the column with the dates
%\setlength{\hintscolumnwidth}{3cm}

% for the 'classic' style, if you want to force the width allocated to your
%   name and avoid line breaks. be careful though, the length is normally
%   calculated to avoid any overlap with your personal info; use this at your
%   own typographical risks...
%\setlength{\makecvtitlenamewidth}{10cm}

% personal data
\name{John}{Evans}

%\title{Resumé title}
% optional, remove / comment the line if not wanted

\address{36 Symphony Road 1A}{Boston, MA  02115}{USA}
\phone[mobile]{+1~(617)~447~0030}                   
\email{john.g.evans.ne@gmail.com}                  
\social[twitter]{johnevans007}                    
\social[github]{quintusdias}                     
%\extrainfo{additional information}             

%\photo[64pt][0.4pt]{picture}
% optional, remove / comment the line if not wanted.
% '64pt' is the height the picture must be resized to,
% 0.4pt is the thickness of the frame around it (put it to 0pt for no frame)
% and 'picture' is the name of the picture file

\hyphenation{MATLAB}

%-------------------------------------------------------------------------------
%            content
%-------------------------------------------------------------------------------
\begin{document}
\makecvtitle

\renewcommand{\cvcomputer}[2]{\cvline{#1}{\small#2}}
\section{Computer skills}
  \cvcomputer{Programming}{Strong in Python (numpy, pandas, matplotlib),
    MATLAB, C/C++, PL/SQL, Bash.  Familiar with R, SAS, \LaTeX, Fortran90,
    XMP/XML.  Past experience with Java, PHP, Perl, Fortran 77}
  \cvcomputer{Software Practices}{Experience with continuous integration,
    writing test plans, unit testing (Python and MATLAB), and software
    version control packages such as Git, Subversion, Perforce, and CVS.}
  \cvcomputer{File Formats and Software Packages}{Extensive experience
    with netCDF, HDF5, HDF4, JPEG2000, CFITSIO, libTIFF, CDF, DICOM,
    NRRD, and NIfTI.  Some experience with OpenJPEG, Kakadu, and IJG
    JPEG libraries.  Several years of MySQL database administration,
    some experience with Oracle, PostgreSQL, SQLite}
  \cvcomputer{Platforms and Systems \mbox{Administration}}{Currently
    working with Fedora, Linux Mint, and Mac OS X.  Past experience configuring
    Mandriva, Scyld, Ubuntu, Digital Unix, Irix, Windows.  Past experience
    configuring Samba, Amanda, Apache, iptables, FLEXLM.}

\section{Open Source Projects}
  \cvlistitem{Glymur:
      \href{glymur.readthedocs.org}{\texttt{http://glymur.readthedocs.org}}}
  \cvlistitem{hdfeos-python-zoo:
      \href{hdfeos.org}{\texttt{http://hdfeos.org}}}
  \cvlistitem{Mexcdf:
      \href{mexcdf.sourceforge.net}{\texttt{http://mexcdf.sourceforge.net}}}
  \cvlistitem{Sunpy:
      \href{www.sunpy.org}{\texttt{http://www.sunpy.org}}}
  \cvlistitem{Python XMP Toolkit:
      \href{python-xmp-toolkit.readthedocs.org}
      {\texttt{http://python-xmp-toolkit.readthedoc.sorg}}}

\section{Education}
\cventry{1992--1995}
    {Master of Science}
    {Montana State University}
    {Bozeman}{}{Computer Science}
\cventry{1988--1990}
    {Master of Science}
    {Montana State University}
    {Bozeman}{}{Mathematics}
\cventry{1984--1998}
    {Bachelor of Science}
    {Montana State University}
    {Bozeman}{}{Applied Mathematics}

\section{Experience}
\cventry{2013 -- 2014}
    {Programmer}
    {Partners Health Care / Bullfinch Medical Group}{Boston, MA}{}{
      Rewrote software pipelines for processing diffusion and DCE medical
      imaging data.  Performed exploratory work on platforms such as
      HubZero  for comparing algorithm performance. Wrote documentation
      and analysis tools for disease propagation model.}
\cventry{2007 -- 2012}
    {Developer}{MathWorks}{Natick, MA}{}
        {Team lead for Image and Scientific Data Formats.  Delivered new
        MATLAB functionality for netCDF, HDF5, JPEG2000, HDF, HDF-EOS,
        FITS, TIFF, and CDF formats, including both high-level and
        low-level interfaces.  Also responsible for day to day maintenance
        of existing support for JPEG, PNG, GIF and various other image
        formats.  Delivered netCDF formal interface feature into MATLAB
        R2008b release, updated for netCDF-4 support in R2010b. Triaged
        bug reports, improved code coverage and quality, and managed
        3rd party library integration and general infrastructure of my
        team's particular software component.  Wrote and presented 6-month
        team planning documents to company management.  Sponsored five
        short-term intra-company internship projects for new engineers.
        Represented MathWorks at annual HDF/NASA Spring Workshops.}
\cventry{2004--2007}
    {Computing Specialist}
    {Institute of Coastal and Marine Science, Rutgers University}
    {New Brunswick, NJ}{}
      {Assisted in setup,  operation, and output analysis  of Regional
      Ocean Model System (ROMS) on various OpenMP and MPI systems.
      This included operational support of a Beowulf Cluster with 20
      dual processor compute nodes, system administration for a number of
      Linux workstations and laptops, administration of a tomcat server.}
\cventry{2003--2004}
    {Computing Specialist}
    {USGS Branch of Atlantic Marine Geology}{Woods Hole, MA}{}
      {Conversion of aging geographic datasets into ESRI grid and
      shape file formats and Created GIS of Gulf of Mexico datasets.}
\cventry{2001--2003}
    {Computing Specialist}
    {School of Marine Science, University of Maine}{Orono, ME}{}
        {Designed and implemented a near real-time buoy processing system
        for data telemetered via both cell phone and GOES satellite
        for GoMOOS (Gulf of Maine Ocean Observing System).   The array
        of instruments included wind sensors, ADCPs, current meters,
        conductivity/temperature recorders, accelerometers, radiometers,
        and fluorometers.   Responsible for MySQL database administration
        and general systems administration of a small network of RedHat
        Linux workstations, Windows PCs, and Macs.   Wrote documentation
        for the processing system and system administrative efforts.
        Also participated in CODAR project for assimilation of RADAR
        into surface current patterns.}
\cventry{1998--2000}
    {Software Engineer}{AER, Inc}{Cambridge, MA}{}
      {Supported the Land Cover, Albedo, NDVI/EVI, and
      Imagery Environmental Data Records (EDRs) within the VIIRS
      project. Integrated new algorithms with legacy codes. Wrote gridding
      routines for sensed data to various common map projections.}
\cventry{1995--1998}
    {Computing Specialist}
    {USGS Branch of Atlantic Marine Geology}{Woods Hole, MA}{}
      {Wrote support software for scientific visualization, modeling,
      and public education. Conversion of old time series data sets into
      standardized netCDF conventions.  Systems administration of Linux,
      Windows, Digital Unix, and Irix systems.}

\section{Languages}
\cvitem{German}{Intermediate}
\cvitem{French}{Beginner}

\section{Volunteer activities}
\cvitem{Zooniverse}
  {Participant in Andromeda, Planet Hunters projects.}
\cvitem{Running Clubs}
  {Assisting in maintenance of Falmouth Track Club and Raritan Valley
   Road Runners web sites.
   President of Somerville Road Runners, June 1998 -- March 1999.}
\cvitem{MSU Athletics}
  {Statistician for Montana State University men's and women's basketball
  teams.}
\cvitem{Museum of the Rockies}
  {Front desk, education, and exhibit construction duties.}

%\clearpage
%%-----       letter       ---------------------------------------------------------
%% recipient data
%\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
%\date{January 01, 1984}
%\opening{Dear Sir or Madam,}
%\closing{Yours faithfully,}

% use an optional argument to use a string other than "Enclosure", or redefine \enclname
%\enclosure[Attached]{curriculum vit\ae{}}

%\makelettertitle
%
% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis
% ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis.
% Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt
% tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula
% volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris
% ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec
% scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa
% at felis accumsan rhoncus.
%
% Suspendisse commodo, massa eu congue tincidunt, elit mauris
% pellentesque orci, cursus tempor odio nisl euismod augue. Aliquam
% adipiscing nibh ut odio sodales et pulvinar tortor laoreet. Mauris
% a accumsan ligula. Class aptent taciti sociosqu ad litora torquent
% per conubia nostra, per inceptos himenaeos. Suspendisse vulputate
% sem vehicula ipsum varius nec tempus dui dapibus. Phasellus et est
% urna, ut auctor erat. Sed tincidunt odio id odio aliquam mattis.
% Donec sapien nulla, feugiat eget adipiscing sit amet, lacinia ut
% dolor. Phasellus tincidunt, leo a fringilla consectetur, felis diam
% aliquam urna, vitae aliquet lectus orci nec velit. Vivamus dapibus
% varius blandit.
%
% Duis sit amet magna ante, at sodales diam. Aenean consectetur
% porta risus et sagittis. Ut interdum, enim varius pellentesque
% tincidunt, magna libero sodales tortor, ut fermentum nunc metus a
% ante. Vivamus odio leo, tincidunt eu luctus ut, sollicitudin sit
% amet metus. Nunc sed orci lectus. Ut sodales magna sed velit volutpat
% sit amet pulvinar diam venenatis.
%
%Albert Einstein discovered that $e=mc^2$ in 1905.
%
%\[ e=\lim_{n \to \infty} \left(1+\frac{1}{n}\right)^n \]
%
%\makeletterclosing
%
% if you are typesetting your resume in Chinese using CJK; the
% \clearpage is required for fancyhdr to work correctly with CJK,
% though it kills the page numbering by making \lastpage undefined
%%\clearpage\end{CJK*}
\end{document}


%% end of file `template.tex'.
