\documentclass[11pt]{moderncv}  % Sets the default text size to 11pt and class
                               % to article.
% moderncv themes
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{casual}

% color options 'blue' (default), 'orange', 'green', 'red', 'purple',
% 'grey' and 'black'
\moderncvcolor{blue}

% to set the default font; use '\sfdefault' for the default sans serif font,
%   '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}

% uncomment to suppress automatic page numbering for CVs longer than one page
%\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% if you want to change the width of the column with the dates
%\setlength{\hintscolumnwidth}{3cm}

% for the 'classic' style, if you want to force the width allocated to your
%   name and avoid line breaks. be careful though, the length is normally
%   calculated to avoid any overlap with your personal info; use this at your
%   own typographical risks...
%\setlength{\makecvtitlenamewidth}{10cm}

% personal data
\name{John}{Evans}

%\title{Resumé title}
% optional, remove / comment the line if not wanted

\address{2901 South 21st Avenue}{Bozeman, MT  59718}{USA}
\phone[mobile]{+1~(617)~447~0030}                   
\email{jevans667cc@proton.me}                  
\social[twitter]{johnevans007}                    
\social[github]{quintusdias}                     
%\extrainfo{additional information}             

%\photo[64pt][0.4pt]{picture}
% optional, remove / comment the line if not wanted.
% '64pt' is the height the picture must be resized to,
% 0.4pt is the thickness of the frame around it (put it to 0pt for no frame)
% and 'picture' is the name of the picture file

\hyphenation{MATLAB administration}

%-------------------------------------------------------------------------------
%            content
%-------------------------------------------------------------------------------
%            content
%-------------------------------------------------------------------------------
\begin{document}

%%-----       letter       ----------------------------------------------------
%% recipient data
\recipient
{Mr. Coltran Hophan-Nichols}
{UIT Research Cyberinfrastructure\\Bozeman, MT 59717}
%\date{January 01, 1984}
\opening{Dear Mr. Hophan-Nichols}
\closing{Sincerely,}

% use an optional argument to use a string other than "Enclosure", or redefine
% \enclname
%\enclosure[Attached]{curriculum vit\ae{}}

\makelettertitle

I would like to place my name into consideration for the role of
System Administrator for Research Cyberinfrastructure in RCI.  My
entire career has been either in software development with an
emphasis on scientific software, operations management, or systems
administration, and when that is combined with my  working relationships
with other system admistrators in the MSU community, I feel that I
have a lot to offer for that position.


Python has become my language of choice over the last few years and has been the primary tool working in GIS Dissemination at the National Weather Service these past three years.  I also have a long history with MATLAB, however.  In 2007, I joined the Image and Scientific Data Formats team at the MathWorks, becoming  team lead after one year.  This give me a broad experience with a variety of open source image and scientific data formats and APIs, ranging from older “classic” formats such as JPEG, FITS, TIFF, and HDF4, to newer and more complex formats such as JPEG2000 and HDF5/netCDF.  In fact, my first assignment at MathWorks was to implement official netCDF support in MATLAB, and this was largely based upon the earlier netCDF community project on SourceForge, MEXCDF, to which I was the prime contributor.   I also authored the R2011a “high-level” HDF5 interface for MATLAB while continuing to refactor and performance-tune the existing “low-level” HDF5 interface.

Working at the MathWorks was a good experience in software engineering practices such as continuous integration, refactoring, requirements gathering, functional design, design reviews including test plans, and long-range planning as the team lead.   There were not too many opportunities for conferences, but for six years I did attend the NASA/HDF Spring Workshop as MathWorks’ representative, where I became well-acquainted with the people of the HDF5 Group.

Upon arriving at the MSU library, I took over administration of six Rocky Linux 8 servers.  My projects have included updating the existing iptables firewall configurations to firewalld, putting into place a reliable tape backup system using Amanda (it may be old software, but it does the job), updating modsecurity rules, annd shepherding a migration of our samba system from local accounts to using MSU Active Directory (work in progress).  On the applications side, I manage Scholarworks, which is the open access repository for the intellectual works at MSU.  As you are aware, this application was migrated from one of the rocky 8 servers to new RHEL 9 VMs in Enterprise Computing.

Thank you for your consideration.  Please do not hesitate to contact me if you require any further information.

\makeletterclosing

\end{document}


%% end of file `template.tex'.
